### 2014-10-16 excersice 1/main.tex
fixed asembler

\usepackage{listings}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{fancyhdr}
\pagestyle{fancy}

@@

\section*{Q4} % 7.2
\begin{enumerate}
\item % a
There is no need to protect the read as if the read returns the wrong value, it will be a lower value than it should and the read can simply be done again.
\item % b 
See listing~\ref{lst:q3b}.

\item % c
See listing~\ref{lst:q3c}.
\end{enumerate}

\lstset{language={[x86masm]Assembler},frame=single}
\lstinputlisting[firstline=20, lastline=33, caption={Sync. using T\&S},label={lst:q3b}]{upgASM.asm}
\lstinputlisting[firstline=37, lastline=43, caption={Sync. using F\&A},label={lst:q3c}]{upgASM.asm}

\section*{Q5} % 7.3
\begin{enumerate}
\item % a
See listing~\ref{lst:q4a}.
\setcounter{enumi}{3}
\item % d
See listing~\ref{lst:q4e}.
\item % e
See listing~\ref{lst:q4d}.
\end{enumerate}

\lstset{language={[x86masm]Assembler},frame=single}
\lstinputlisting[firstline=0, lastline=4, caption={F\&ADD X, Rx, a},label={lst:q4a}]{upgASM.asm}

\lstinputlisting[firstline=6, lastline=10, caption={SWAP(Rx, X)},label={lst:q4e}]{upgASM.asm}

\lstinputlisting[firstline=12, lastline=18, caption={CAS Rx, Ry, X},label={lst:q4d}]{upgASM.asm}

>>>>

\usepackage{listings}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\pagestyle{fancy}

@@

\section*{Q4} % 7.2
\begin{enumerate}
\item % a
There is no need to protect the read as if the read returns the wrong value, it will be a lower value than it should and the read can simply be done again.
\item % b 
See listing~\ref{lst:q4b}.

\item % c
See listing~\ref{lst:q4c}.
\end{enumerate}

\lstset{language={[x86masm]Assembler},frame=single}
\lstinputlisting[firstline=24, lastline=36, caption={Sync. using T\&S},label={lst:q4b}]{upgASM.asm}
\lstinputlisting[firstline=39, lastline=44, caption={Sync. using F\&A},label={lst:q4c}]{upgASM.asm}

\section*{Q5} % 7.3
\begin{enumerate}
\item % a
See listing~\ref{lst:q5a}.
\setcounter{enumi}{3}
\item % d
See listing~\ref{lst:q5d}.
\item % e
See listing~\ref{lst:q5e}.
\end{enumerate}

\lstset{language={[x86masm]Assembler},frame=single}
\lstinputlisting[firstline=2, lastline=5, caption={F\&ADD X, Rx, a},label={lst:q5a}]{upgASM.asm}

\lstinputlisting[firstline=8, lastline=12, caption={SWAP(Rx, X)},label={lst:q5d}]{upgASM.asm}

\lstinputlisting[firstline=15, lastline=21, caption={CAS Rx, Ry, X},label={lst:q5e}]{upgASM.asm}
